True versus apparent shapes of astrophysical bow shocks

### 2016-05-26 papers/Paper1/sec-application.tex
Update text in sections 4 and 5
In conics section, just corrected a typo which prevents compiling
In applications section. Included a brief description about observations

%We measured the Characteristic radii in Orion Nebula proplyds from observations with the ACS camera from the Hubble Space Telescope (HST) using a lamp filter around $\lambda = 5007 \AA$. The proposal for these observations were done by  Jogee, S. in 2004 with calibration purposes but (he never published anything using explicitly these observations). % We must check if this phrase should be included
%Nevertheless, as we are only interested in measure the geometric shape of bow shocks, these observations are more than enough.

>>>>

We measured the Characteristic radii in Orion Nebula proplyds from observations with the WPC2 camera from the Hubble Space Telescope (HST) using the narrow [OIII] filter. The original proposal were done by John Bally (The proposal ID is 5469). In figure \ref{fig:radii-measures-example}, we show the field where our proplyds sample lies with the measurements of each bow shock shape we made.

### 2016-05-26 papers/Paper1/sec-conic.tex
Rearrange of some equations and introducing new
The idea is to derive R90 and theta_c from characteristic radii
more naturally
Update text in sections 4 and 5
In conics section, just corrected a typo which prevents compiling
In applications section. Included a brief description about observations

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
\begin{align}
x = a\Cos(t)-x_0 \label{eq:par-x}\\ 
y = b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) = \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) = \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi < t < \pi \\
R_0 = a - x_0 \\
a<0 ~ \mathrm{for~hyperbola}
\end{align}
We have set a whole family of curves with a singular parameter denoted as $\tan\theta_c \equiv \frac{b}{a}$. Positive values of this parameter describe closed curves
(i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas). Particular cases are $\theta_c =\frac{\pi}{4}$, which describes a circle and $\theta_c=0$, which describes
a parabola.
To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,$\theta_c$)$
could be derived from the former. The transformation betwwen the conic parameters and the characteristic radii are given by:
\begin{align}
\frac{R_c}{D} &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
\frac{R_{90}}{D} &= b\left(1 \mp \frac{(R_0-a)^2}{a^2}\right)
\end{align}
The inverse transformation is given by:
\begin{align}
a &= (not finished) \label{eq:a-conic}\\
b &= \left(aR_c\right)^{1/2}\\
\theta_c &= \left|B^2 - 2A\right|^{1/2} \label{eq:thc-conic} 
\end{align}
From equations (\ref{eq:a-conic}) we can see that for $R^2_{90} > 2 R_c$, the conic parameter $a$ is negative, so in this case the resulting conic is an hyperbola, and we must take the negative root
in equation (\ref{eq:thc-conic}). The opposite applies for ellipses.
will be an ellipse
\subsection{Plane-of-sky projection of conic sections} 
\begin{figure*}
\includegraphics[width=0.9\linewidth]{annotated}
\caption{Projected Radius of curvature vs projected $R_0$ for $\theta_c=60^\circ,45^\circ,28^\circ, 0^\circ,-15^\circ,-30^\circ$. Each colored points represent
the same shape at a different inclination. Being the dark blue the ones with the lower inclination and the red ones with the highest value. For closed shapes, there is
an assymptotic limit for the projected radius of curvature at high inclinations, while for open shapes there is an upper limit for inclination where a tangent line can be observed.}
\label{fig:Apqp}
\end{figure*}

>>>>

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
\begin{align}
x = a\Cos(t)-x_0 \label{eq:par-x}\\ 
y = b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) = \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) = \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi < t < \pi \\
R_0 = a - x_0 \\
a<0 ~ \mathrm{for~hyperbola}
\end{align}
We have set a whole family of curves with a singular parameter denoted as $\tan\theta_c \equiv \frac{b}{a}$. Positive values of this parameter describe closed curves
(i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas). Particular cases are $\theta_c =\frac{\pi}{4}$, which describes a circle and $\theta_c=0$, which describes
a parabola.
To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,\theta_c)$
could be derived from the former. The transformation between the conic parameters and the characteristic radii are given by:
\begin{align}
\frac{R_c}{D} &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
\frac{R_{90}}{D} &= b\left(1 \mp \frac{(R_0-a)^2}{a^2}\right)
\end{align}
The inverse transformation is given by:
\begin{align}
a &= \frac{R_c}{2A-B^2} \label{eq:a-conic}\\
b &= \left(aR_c\right)^{1/2}\\
\theta_c &= \left|B^2 - 2A\right|^{1/2} \label{eq:thc-conic} \\
\mathrm{where:}& B\equiv \frac{R_{90}}{R_0} \\
A \equiv \frac{R_c}{R_0}
\end{align}
From equations (\ref{eq:a-conic}) we can see that for $R^2_{90} > 2 R_c$, the conic parameter $a$ is negative, so in this case the resulting conic is an hyperbola, and we must take the negative root
in equation (\ref{eq:thc-conic}). The opposite applies for ellipses.
\subsection{Plane-of-sky projection of conic sections} 
\begin{figure*}
\includegraphics[width=0.9\linewidth]{annotated}
\caption{Projected Radius of curvature vs projected $R_0$ for $\theta_c=60^\circ,45^\circ,28^\circ, 0^\circ,-15^\circ,-30^\circ$. Each colored points represent
the same shape at a different inclination. Being the dark blue the ones with the lower inclination and the red ones with the highest value. For closed shapes, there is
an assymptotic limit for the projected radius of curvature at high inclinations, while for open shapes there is an upper limit for inclination where a tangent line can be observed.}
\label{fig:Apqp}
\end{figure*}
